% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Nicholas Sullivan-Friedman}

\basicInfo{
  \email{nicholas@rpgcubed.com} \textperiodcentered\ 
  \phone{(+1) 415 328-9195} %\textperiodcentered\ 
  %\linkedin[billryan8]{https://www.linkedin.com/in/billryan8}
  }

\section{\faInfoCircle\ Abstract}


\section{\faUsers\ Experience}
\datedsubsection{\textbf{Tenka Labs, Inc.} San Rafael, CA}{Jun. 2017 -- Sept. 2018}
\role{Controller / Internal IT Support}{Manager: Audrey Donaldson (CEO, former)}
Managed company financials and controls. Supported business projects with internal tools and processes. Various other responsibilities as needed, due to the early-stage nature of the company.
\begin{itemize}
  \item 
  \item Provided reports and analyses to assist management.
  \item Handled day-to-day bookkeeping.
\end{itemize}

% \datedsubsection{\textbf{Tenka Labs, Inc.} San Rafael, CA}{Mar. 2017 -- Jun. 2018}
% \role{Consultant}{Manager: Nathaniel MacDonald (CEO, former)}
% Managed company interns. Assisted with various business projects.
% \begin{itemize}
%   \item Scheduled and managed interns.
%   \item Basic bookkeeping/data-entry.
% \end{itemize}

\datedsubsection{\textbf{Bay Sprouts, LLC. DBA Bean Sprouts} Sausalito, CA}{Dec. 2015 -- Jun. 2017}
\role{Assistant General Manager}{Manager: Jonathan Craft (GM)}
Managed day-to-day operations of a 
\begin{itemize}
  \item Handled staffing and employee management for staff of 10-20.
  \item Reduced wastage from >10\% to <3\% of revenue via various inventory management and operational improvements.
  \item Assisted with annual budget determination and allocation.
\end{itemize}


% Reference Test
% \datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
% An xxx optimized for xxx\cite{verma2015large}
% \begin{itemize}
%  \item main contribution
% \end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Certified Food Manager (ServSafe)
  \item Programming Languages: Python == 
  \item Platform: Windows > Linux > macOS
  \item Development: Mobile(Native/Flutter) == Web
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/carlank
  \item Languages: English (C2/Native), Spanish (B1)
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
