% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
% \usepackage{showframe} % Debugging
\usepackage[none]{hyphenat}
\frenchspacing

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Nicholas Sullivan-Friedman}

\basicInfo{
  \email{nicholas@rpgcubed.com} \textperiodcentered\ 
  \phone{(+1) 415 328-9195} %\textperiodcentered\ 
  %\linkedin[billryan8]{https://www.linkedin.com/in/billryan8}
  }

\section{\faInfoCircle\ Abstract}
Goal-oriented systems analyst and efficiency specialist with over three years of experience working with small businesses to improve their internal workflows. Highly educable with a passion for learning and problem-solving. Diverse technical skills including network administration, database management, and software development.

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Tenka Labs, Inc.} San Rafael, CA}{June 2017 -- September 2018}
\role{Controller / Internal IT Support}{Manager: Audrey Donaldson (CEO)}
Managed financials and controls of a \$4MM educational toy startup. Supported business projects with internal tools and processes. Various other responsibilities as needed, due to the early-stage nature of the company.
\begin{itemize}
  \item Assisted with website and mobile app maintenance and development, among other technical projects.
  \begin{itemize}
    \item Administered DNS and hosting services for company website.
    \item Developed MVP of cross-platform version of app, via Flutter (Dart) rewrite.
    \item Handled day-to-day administration of most internal networks, devices, services, and utilities.
  \end{itemize}
  \item Assisted with EDI configuration and management.
  \item Provided reports and analyses to assist the executive team.
  \item Handled day-to-day accounting, incl. payroll.
  \item Liased with 3PL, vendors, and other operational partners.
  \item Provided customer support, typically in a T1/T2 capacity.
  \item Designed and implemented relocation plan, reducing monthly rent expenses by 62\%.
\end{itemize}

% \datedsubsection{\textbf{Tenka Labs, Inc.} San Rafael, CA}{March 2017 -- June 2018}
% \role{Consultant}{Manager: Nathaniel MacDonald (CEO, former)}
% Managed company interns. Assisted with various business projects.
% \begin{itemize}
%   \item Scheduled and managed interns.
%   \item Basic bookkeeping/data-entry.
% \end{itemize}

\datedsubsection{\textbf{Bay Sprouts, LLC. DBA Bean Sprouts} Sausalito, CA}{December 2015 -- June 2017}
\role{Assistant General Manager}{Manager: Jonathan Craft (GM)}
Managed day-to-day operations of a \$1MM annual revenue quick-service restaurant.
\begin{itemize}
  \item Worked with vendors and partners to build relationships and the company brand.
  \item Installed and maintained POS system (Breadcrumbs, acquired by Upserve during employment).
  \item Assisted with annual budget determination and allocation.
  \item Handled staffing, training, and employee management for team of 10-20.
  \item Reduced shrinkage from over 10\% to less than 3\% of gross revenue via various inventory and operational improvements.
  \begin{itemize}
    \item Implemented perpetual inventory analysis to determine deviation from expected use.
    \item Implemented JIT principles to minimize loss from forecasting errors.
  \end{itemize}
\end{itemize}


% Reference Test
% \datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
% An xxx optimized for xxx\cite{verma2015large}
% \begin{itemize}
%  \item main contribution
% \end{itemize}

\section{\faCogs\ Skills and Certifications}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Javascript (incl. Node.js) > Python > (Dart > Kotlin/Java > C++ > Swift/ObjC)
  \item Applications/Services: MS Office Suite, Adobe CC, Zendesk, Quickbooks, Sublime Text 3.\\ Familiar with many other common utilities and tools.
\end{itemize}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   % \item GitHub: https://github.com/carlank
%   \item Languages: English (Native), Spanish (Limited Working Proficiency)
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
