% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
% \usepackage{showframe} % Debugging
\usepackage[none]{hyphenat}
\frenchspacing

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Nicholas Sullivan-Friedman}

\basicInfo{
  \email{nicholas@rpgcubed.com} \textperiodcentered\ 
  \phone{(+1) 415 328-9195} %\textperiodcentered\ 
  %\linkedin[billryan8]{https://www.linkedin.com/in/billryan8}
  }

\section{\faInfoCircle\ Abstract}
Educable autodidact with a passion for learning and AI. 

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Tenka Labs, Inc.} San Rafael, CA}{June 2017 -- September 2018}
\role{Controller / Internal IT Support}{Manager: Audrey Donaldson (CEO)}
Managed company financials and controls. Supported business projects with internal tools and processes. Various other responsibilities as needed, due to the early-stage nature of the company.
\begin{itemize}
  \item Provided reports and analyses to assist the executive team.
  \item Handled day-to-day accounting, incl. payroll.
  \item Liased with 3PL, vendors, and other operational partners.
  \item Assisted with EDI configuration and management.
  \item Assisted with website and mobile app maintenance and development, among other technical projects.
  \item Designed and implemented relocation plan, reducing monthly rent expenses by 62\%.
  \item Provided customer support as needed.
\end{itemize}

% \datedsubsection{\textbf{Tenka Labs, Inc.} San Rafael, CA}{March 2017 -- June 2018}
% \role{Consultant}{Manager: Nathaniel MacDonald (CEO, former)}
% Managed company interns. Assisted with various business projects.
% \begin{itemize}
%   \item Scheduled and managed interns.
%   \item Basic bookkeeping/data-entry.
% \end{itemize}

\datedsubsection{\textbf{Bay Sprouts, LLC. DBA Bean Sprouts} Sausalito, CA}{December 2015 -- June 2017}
\role{Assistant General Manager}{Manager: Jonathan Craft (GM)}
Managed day-to-day operations of a \$1MM annual revenue quick-service restaurant.
\begin{itemize}
  \item Handled staffing, training, and employee management for team of 10-20.
  \item Reduced shrinkage from over 10\% to less than 3\% of gross revenue via various inventory and operational improvements.
  \begin{itemize}
    \item Implemented perpetual inventory analysis to determine deviation from expected use.
    \item Implemented JIT principles to minimize loss from forecasting errors.
    \item Refined line ergonomics to improve portioning consistency.
  \end{itemize}
  \item Assisted with annual budget determination and allocation.
  \item Installed and maintained POS system (Breadcrumbs, acquired by Upserve during employment).
  \item Worked with vendors and partners to build relationships and the company brand.
\end{itemize}


% Reference Test
% \datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
% An xxx optimized for xxx\cite{verma2015large}
% \begin{itemize}
%  \item main contribution
% \end{itemize}

\section{\faCogs\ Skills and Certifications}
\begin{itemize}[parsep=0.5ex]
  \item POS Systems: Breadcrumbs(Upserve), Micros, Clover
  \item Certified Food Manager (ServSafe)
  \item Programming Languages: Python > Dart > C > Other
  \item Specific Applications: Advanced Excel and Quickbooks, moderate Zendesk administration. Familiar with many common utilities.
\end{itemize}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   % \item GitHub: https://github.com/carlank
%   \item Languages: English (Native), Spanish (Limited Working Proficiency)
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
